Comparing ChatGPT-4 to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-02-07 manuscript/manuscript.tex
Add results figures for age groups

\begin{figure}[h!]
\centering
\includegraphics[width=0.7\textwidth]{fig-perf-agerange-adult.pdf}
\caption{Model performance for assigning causes of death in the adult age group (12 to 69 Years) by five-year age ranges. PCCC values are sorted by the highest to lowest PCCC for each age range. Only models with PCCC values close to the highest and lowest PCCC are shown.}\label{fig-perf-agerange-adult}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.7\textwidth]{fig-perf-cod-adult.pdf}
\caption{Model performance for assigning causes of death in the adult age group (12 to 69 Years) by five-year age ranges. PCCC values are sorted by the highest to lowest PCCC for each age range. Only models with PCCC values close to the highest and lowest PCCC are shown.}\label{fig-perf-agerange-adult}
\end{figure}

@@

@@

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=0.7\textwidth]{fig-perf-agerange-adult.pdf}
\caption{Model performance for adult records by age range. ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA model performance for assigning CODs in the adult age group (12 to 69 Years) by five-year age ranges. PCCC values are sorted by the highest to lowest PCCC for each age range. Only models with PCCC values within .05 of the highest and lowest PCCC are shown.}\label{fig-perf-agerange-adult}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.7\textwidth]{fig-perf-cod-adult.pdf}
\caption{Model performance for adult records by COD. ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA model performance for assigning CODs in the adult age group (12 to 69 Years) by COD. PCCC values are sorted by the highest to lowest PCCC for each age range. Only models with PCCC values within .05 of the highest and lowest PCCC are shown.}\label{fig-perf-cod-adult}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.7\textwidth]{fig-perf-agerange-child.pdf}
\caption{Model performance for child records by age range. ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA model performance for assigning CODs in the child age group (28 days to 11 years) by five-year age ranges. PCCC values are sorted by the highest to lowest PCCC for each age range. Only models with PCCC values within .05 of the highest and lowest PCCC are shown.}\label{fig-perf-agerange-child}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.7\textwidth]{fig-perf-cod-child.pdf}
\caption{Model performance for child records by COD. ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA model performance for assigning CODs in the child age group (28 days to 11 years) by COD. PCCC values are sorted by the highest to lowest PCCC for each age range. Only models with PCCC values within .05 of the highest and lowest PCCC are shown.}\label{fig-perf-cod-child}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.7\textwidth]{fig-perf-agerange-neo.pdf}
\caption{Model performance for neonatal records by age range. ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA model performance for assigning CODs in the neonatal age group (under 28 days) by five-year age ranges. PCCC values are sorted by the highest to lowest PCCC for each age range. Only models with PCCC values within .05 of the highest and lowest PCCC are shown.}\label{fig-perf-agerange-neo}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.7\textwidth]{fig-perf-cod-neo.pdf}
\caption{Model performance for neonatal records by COD. ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA model performance for assigning CODs in the neonatal age group (under 28 years) by COD. PCCC values are sorted by the highest to lowest PCCC for each age range. Only models with PCCC values within .05 of the highest and lowest PCCC are shown.}\label{fig-perf-cod-neo}
\end{figure}
